### 2020-01-08 README.Rmd
fix-error-in-unlist-in-temperature
lifecycle-badge

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/gosset)](https://cran.r-project.org/package=gosset)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/agrobioinfoservices/gosset?branch=master&svg=true)](https://ci.appveyor.com/project/kauedesousa/gosset)
[![Build Status](https://travis-ci.org/agrobioinfoservices/gosset.svg?branch=master)](https://travis-ci.org/agrobioinfoservices/gosset)
[![codecov](https://codecov.io/gh/agrobioinfoservices/gosset/master.svg)](https://codecov.io/github/agrobioinfoservices/gosset?branch=master)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![GPLv3 license](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.r-project.org/Licenses/GPL-3)
<!-- badges: end -->

@@

```r

library("devtools")
devtools::install_github("agrobioinfoservices/gosset", build_vignettes = TRUE)

```

@@

```r

vignette("Overview", package = "gosset")

```

>>>>

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/gosset)](https://cran.r-project.org/package=gosset)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/agrobioinfoservices/gosset?branch=master&svg=true)](https://ci.appveyor.com/project/kauedesousa/gosset)
[![Build Status](https://travis-ci.org/agrobioinfoservices/gosset.svg?branch=master)](https://travis-ci.org/agrobioinfoservices/gosset)
[![codecov](https://codecov.io/gh/agrobioinfoservices/gosset/master.svg)](https://codecov.io/github/agrobioinfoservices/gosset?branch=master)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![GPLv3 license](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.r-project.org/Licenses/GPL-3)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

@@

```r
library("devtools")
devtools::install_github("agrobioinfoservices/gosset", build_vignettes = TRUE)
```

@@

```r
vignette("Overview", package = "gosset")
```
